The \dealii{} Library, Version 9.4

### 2022-06-23 9.4/paper.tex

\texttt{CGALWrappers::compute\_quadrature\_on\_boolean\_operation()} returns a \texttt{Quadrature<3>} that allows exact integration on polyhedral elements coming out of a \texttt{BooleanOperation} between \dealii cells.
The quadrature rule is built by meshing the polyhedral region with tetrahedra, computing on each tetrahedron a \texttt{QGaussSimplex<3>} quadrature rule by using \texttt{QSimplex<3>::\allowbreak{}compute\_affine\_transformation()}, and finally
collecting all of the rules together, giving a \texttt{Quadrature<3>} formula on the \emph{physical} element.

>>>>

\texttt{CGALWrappers::compute\_quadrature\_on\_boolean\_operation()} returns a \texttt{Quadrature<3>} that allows exact integration of polynomials on polyhedral elements coming out of a \texttt{BooleanOperation} between \dealii cells.
The quadrature rule is built by meshing the polyhedral region with tetrahedra, computing on each tetrahedron a \texttt{QGaussSimplex<3>} quadrature rule by using \texttt{QSimplex<3>::\allowbreak{}compute\_affine\_transformation()}, and finally
collecting all of the rules together, giving a \texttt{Quadrature<3>} formula on the \emph{physical} element.
